Discovering constraints in spreadsheets and tabular data

### 2016-09-07 Paper/ECAI/tabular.tex
add contributions, rework abstract

\title{Learning constraints in spreadsheets and tabular data}
% see http://www.acm.org/binaries/content/assets/publications/article-templates/sig-alternate-sample.tex

\author{Name1 Surname1 \and Name2 Surname2 \and Name3 Surname3 \institute{----------------------} }

@@

\begin{abstract}
  \sergey{Samuel! Add a reference to python-constraint somewhere, including the references list at the end}\\
Spreadsheets, CSV (comma separated value) files and other tabular data representations are in wide use today.
However, modeling, maintaining and discovering formulas in tabular data and spreadsheets can be time consuming and error-prone.
In this work, we investigate the automatic discovery of constraints (formulas and relations) in raw tabular data.
We see multiple promising applications for this technique, e.g. in rediscovering constraints, auto-completion and error checking.
Our method takes inspiration from inductive logic programming, constraint learning and constraint satisfaction.
Common spreadsheet functions are represented as predicates whose arguments must satisfy a number of constraints.
Constraint learning techniques are used to identify the predicates that hold between blocks of rows and columns of the tables.
We show that our approach is able to accurately discover constraints in spreadsheets from various sources.
\end{abstract}

@@

@@

This paper is organized as follows.
Section \ref{sec:formalization} introduces concepts relevant to our approach and our problem statement. Section \ref{sec:related_work} presents a more detailed discussion of the related work. Section \ref{sec:approach} presents our approach. Section \ref{sec:evaluation} presents the evaluation of the approach. Section \ref{sec:applications} shows how our system can be used for applications.  Section \ref{sec:conclusions} provides conclusions.

@@

\paragraph{Visual}
The above assumptions do not hold for many tables. However, since the specification of tables is usually easy for humans, we propose a second approach which allows users to indicate tables using a visual tool (screenshots are available in the accompanying github repository with meta-data\footnote{\url{https://github.com/SergeyParamonov/TaCLe}\label{github-link}}).
Users select tables excluding the header and optionally specify an orientation.
The tool then generates the specification of the tables automatically.

@@

We focus on \textit{functional} constraints that could be used as formulas in spreadsheets, ignoring the structural constraints \textit{ALLDIFFERENT}, \textit{FOREIGNKEY} and \textit{PERMUTATION}.
Moreover, we included detected equalities as intended constraints (in 5~spreadsheets).
All experiments were run using Python 3.5.1 on a Macbook Pro, Intel Core i7 2.3~GHz with 16GB RAM.

>>>>

\title{Discovering constraints in spreadsheets and tabular data}
% see http://www.acm.org/binaries/content/assets/publications/article-templates/sig-alternate-sample.tex

\author{} % \institute{----------------------} }

@@

\begin{abstract}
Spreadsheets, CSV (comma separated value) files and other tabular data representations are in wide use today.
However, writing, maintaining and identifying good formulas for tabular data and spreadsheets can be time consuming and error-prone.
In this work, we investigate the automatic discovery of constraints (formulas and relations) in raw tabular data in an unsupervised way.
Common spreadsheet formulas are represented as predicates whose arguments must satisfy the inherent properties of the function. The challenge is to discover these without user information or training examples. % Knowledge discovery
We propose a two-stage generate and test method where the first stage uses constraint solving techniques to efficiently reduce candidates in a generic way based on the function signature. 
Our approach to this knowledge discovery task takes inspiration from inductive logic programming, constraint learning and constraint satisfaction.
We show that we are able to accurately discover constraints in spreadsheets from various sources.
\end{abstract}

@@

Our contributions are as follows:
\begin{itemize}
\item we define the tabular constraint learning problem, where the goal is to learn constraints (functions and relations) that range over entire rows or columns. This is an unsupervised learning problem;
\item we propose a 2-stage generate and test method that reasons for each candidate constraint over the maximally contiguous submatrices in the first stage, and only in the second stage looks at individual rows and columns and their content;
\item furthermore, in the first stage we use a constraint solver to efficiently enumerate all tuples of submatrices compatible with the candidate constraint its arguments, using backtracking search and forward checking;
\item experiments on a range of publicly available spreadsheets show that the system is able to extract constraints with high precision and recall in an unsupervised manner. 
\end{itemize}

@@

This paper is organized as follows.
Section \ref{sec:related_work} presents a detailed discussion of the related work. Section \ref{sec:formalization} introduces concepts relevant to our approach and our problem statement.  Section \ref{sec:approach} presents our approach. Section \ref{sec:evaluation} presents the evaluation of the approach. Section \ref{sec:applications} shows how our system can be used for applications.  Section \ref{sec:conclusions} provides conclusions.

@@

\paragraph{Visual}
\sergey{Luc, can you check if the supplementary material at github is understandable for people? Do we have to add anything there like write that code would be available after?} The above assumptions do not hold for many tables. However, since the specification of tables is usually easy for humans, we propose a second approach which allows users to indicate tables using a visual tool (screenshots are available in the accompanying github repository with meta-data\footnote{\url{https://github.com/SergeyParamonov/TaCLe}\label{github-link}}).
Users select tables excluding the header and optionally specify an orientation.
The tool then generates the specification of the tables automatically.

@@

We focus on \textit{functional} constraints that could be used as formulas in spreadsheets, ignoring the structural constraints \textit{ALLDIFFERENT}, \textit{FOREIGNKEY} and \textit{PERMUTATION}.
Moreover, we included detected equalities as intended constraints (in 5~spreadsheets).
All experiments were run using Python 3.5.1 on a Macbook Pro, Intel Core i7 2.3~GHz with 16GB RAM.
\sergey{Samuel! Add a reference to python-constraint, including the references list at the end}\\
